Manuscript title here

### 2021-10-27 doc/ms/ms.Rmd
updating manuscript adding figure of relationship between PB and M

<!--- warming and effects in food webs --->
Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
[@walther2002]. Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001]. While a growing body of theoretical and
empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010]. Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.

<!--- Speeding up of food web: Species levels--->
Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012]. The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019] and the acquisition and allocation of resources among species [@zhang2017]. Importantly,  --macroecology of food web dynamics and stability are controlled by the

@@

Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
[@ogorman2012; @hood2018]. Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020]. As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams. We, further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities. The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size. 
# Methods

@@

We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous
study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
manipulation [see @nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected fiver Surber samples
(0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10--15 x magnification).
For particularly large samples, fine fractions were subsampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
taxonomic keys [@peterson1977; @merritt2008; @andersen2013]. Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.

@@

Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @benke2017]. Growth rates were determined using taxon appropriate
approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., Radix balthica, etc.) were determined using *in situ* chambers [@huryn1986].
Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned
chambers for 7--15 days, after which they were again photographed. Individual lengths were measured from field pictures using image analysis software [@schindelin2012], and body
lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke1999; @ogorman2012; @hannesdottir2013]. Growth rates (*g*, d^-1^) were
calculated by the changes in mean body size (*W*) over a given time interval (*t*) with the following equation:

@@

Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 1000). For taxa which exhibit synchronous growth
and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017]. Individual Lengths were converted to mg AFDM using published length-mass regression cited
above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
replacement (*n* = 1000) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean
interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
taxon to calculate total population-level production. Intervals were summed to estimate annual secondary production.

@@

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz], given the number of species and the relative distribution of energy fluxes within a community. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings). Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times. The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains. This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative energy flux.

@@

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).

@@

The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 5). Skew towards larger body sizes was negatively associated with stream temperature. The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase. The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 4). Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature. The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).

@@

[@diaz] SAD are more uneven than their statistical background

>>>>

<!--- warming and effects in food webs --->
Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
[@walther2002]. The effects of temperature on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001].

<!--- Speeding up of food web: Species levels--->
Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012].

The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019] and the acquisition and allocation of resources among species [@zhang2017]. Importantly,  --macroecology of food web dynamics and stability are controlled by the

@@

Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
[@ogorman2012; @hood2018]. Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020]. As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams. We further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities. The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.

# Methods

@@

We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous
study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
manipulation [see @nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected fiver Surber samples
(0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10--15 x magnification).
For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
taxonomic keys [@peterson1977; @merritt2008; @andersen2013]. Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.

@@

Daily secondary production of invertebrate taxa was calculated using the instantaneous growth rate method [IGR; @benke2017]. Growth rates were determined using taxon appropriate
approaches described in [@junker2020]. Briefly, growth rates of common taxa (e.g., Chironomidae spp., *Radix balthica*, etc.) were determined using *in situ* chambers [@huryn1986].
Multiple individuals (*n* = 5--15) within small size categories (\~1 mm length range) were photographed next to a field micrometer, placed into the stream within pre-conditioned
chambers for 7--15 days, after which they were again photographed. Individual lengths were measured from field pictures using image analysis software [@schindelin2012], and body
lengths were converted to mass (mg ash-free dry mass [AFDM]) using published length-mass regressions [@benke1999; @ogorman2012; @hannesdottir2013]. Growth rates (*g*, d^-1^) were
calculated by the changes in mean body size (*W*) over a given time interval (*t*) with the following equation:

@@

Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 1000). For taxa which exhibit synchronous growth
and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017]. Individual Lengths were converted to mg AFDM using published length-mass regression cited
above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
replacement and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration, size-specific growth rates were multiplied by mean
interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
taxon to calculate total population-level production. Intervals were summed to estimate annual secondary production.

@@

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz2021], given the number of species and the relative distribution of energy fluxes within a community. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings). Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times. The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains. This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative energy flux.

@@

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^-1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).

@@

The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 4). Skew towards larger body sizes was negatively associated with stream temperature. The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase. The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 4). Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature. The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).

@@

[@diaz2021] SAD are more uneven than their statistical background
While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010]. Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.
